Untitled

### 2020-10-18 manuscript/manuscript.Rmd
Add requested tables and figures

>>>>

```{r}
p <- PartialDependence(final, vars = ordered_vars, output = "list", rawdata = TRUE)
source("../get_signs.R")
the_signs <- t(get_signs(p))
# Number variables
p <- lapply(1:length(p), function(i){
  p[[i]]+facet_grid(.~Variable, labeller = labeller(
    Variable = setNames(paste0(i, ". ", ordered_vars[i]), ordered_vars[i])
  ))
})

# Reduce font size
p <- lapply(p, function(x){ x + theme(strip.text.x = element_text(size = 6),
                                      axis.text.x = element_text(size = 6),
                                      axis.text.y = element_text(size = 6))})

p_pdp <- metaforest:::merge_plots(p)
ggsave(
  filename = "rf_pdp_numbered.png",
  p_pdp,
  device = "png")
svg("rf_pdp_numbered.svg")
eval(p_pdp)
dev.off()

dirs <- data.frame(the_signs)
VI <- sort(final$forest$variable.importance, decreasing = TRUE)
VI <- data.frame(Variable = paste0(1:length(VI), ". ", names(VI)), Importance = VI, Direction = dirs$V9[match(names(VI), dirs$V1)])
VI$Variable <- ordered(VI$Variable, levels = rev(VI$Variable))
VI$Direction <- ordered(VI$Direction, levels = c("Positive monotonous", "Mostly positive", "Other", "Mostly negative", "Negative monotonous"))

p_vi <- ggplot(VI, aes_string(y = "Variable", x = "Importance")) + 
  geom_segment(aes_string(x = 0, xend = "Importance", 
                          y = "Variable", yend = "Variable"), colour = "grey50", 
               linetype = 2) +
  geom_vline(xintercept = 0, colour = "grey50", 
             linetype = 1) +
  xlab("Permutation Importance") + 
  theme_bw() + theme(panel.grid.major.x = element_blank(), 
                     panel.grid.minor.x = element_blank(),
                     axis.title.y = element_blank(),
                     axis.text.y = element_text(hjust=0)) + 
  geom_point(aes_string(fill = "Direction"), shape = 21, size = 2) + 
  scale_fill_grey(start = 1, end =0) +
  #scale_fill_manual(values = c("Mostly positive" = "white", "Mostly negative" = "gray80", "Negative" = "black", "Other" = "gray50")) + 
  theme(legend.position = c(0.8, 0.2))
ggsave(
  filename = "varimp.png",
  p_vi,
  device = "png")
svg("varimp.svg")
eval(p_vi)
dev.off()

imp_p <- ranger::importance_pvalues(final$forest, formula = .outcome ~., data = final$data, method = "altmann")
VI$pvalue <- imp_p[,2][match(rownames(VI), rownames(imp_p))]
write.csv(VI, "table4.csv", row.names = FALSE)
metaforest:::predict.MetaForest()
df <- as.data.frame(data[data$id %in% tmp, match(names(final$data)[-1], names(data))])
pred <- predict(final, data = df)
write.table(pred$predictions, "clipboard", sep = "\n")
```
